Calendar-based graphics for visualizing people's daily schedules

### 2017-08-08 main.Rmd
updated after today's meeting
update caption

\begin{equation}
  \begin{aligned}
  i &= \lceil (g \mod 35) / 7\rceil, \\
  j &= g \mod 7. \label{eq:grid}
  \end{aligned}
\end{equation}

@@

(ref:year-diagram-cap) Illustration of the indexing layout for months of one year. $M,N$ indicate number of rows and columns, $b$ is a space parameter separating cells.

@@

The algorithm described in Section \ref{sec:algorithm} is for the most common calendar layout, the "monthly" calendar, but it can be simplified to accommodate two other types calendar formats. One is comprised of days of a week in columns and weeks of a year in rows, and the other is days of a month in columns and months of a year in rows, which we refer to as the "weekly" and "daily" calendar, respectively. The layout to be used is controlled by the \code{calendar} argument. The weekly calendar puts more emphasis on days of a week over days of a year, whereas the daily calendar does the opposite. The monthly calendar can be considered as the advanced variant of both weekly and daily. Temporal patterns motivate which variant should be employed. The weekly calendar is appropriate if most of the variation can be characterised by days of the week. On the other hand, the daily calendar should be used when there is a yearly effect but not a weekly effect in the data (for example weather data). When both effects are present, the monthly calendar would be a better choice.

>>>>

\begin{equation}
  \begin{aligned}
  i &= \lceil (g \text{ mod } 35) / 7\rceil, \\
  j &= g \text{ mod } 7. \label{eq:grid}
  \end{aligned}
\end{equation}

@@

(ref:year-diagram-cap) Illustration of the indexing layout for months of one year, where $M$ and $N$ indicate number of rows and columns, $b$ is a space parameter separating cells.

@@

The algorithm described in Section \ref{sec:algorithm} is for the most common calendar layout, the "monthly" calendar, but it can be simplified to accommodate two other types calendar formats. One is comprised of days of a week in columns and weeks of a year in rows, and the other is days of a month in columns and months of a year in rows, which we refer to as the "weekly" and "daily" calendar, respectively. The layout to be used is controlled by the \code{calendar} argument. The weekly calendar puts more emphasis on days of a week over days of a year, whereas the daily calendar does the opposite. The monthly calendar can be considered as the advanced variant of both weekly and daily. Temporal patterns motivate which variant should be employed. The weekly calendar is appropriate if most of the variation can be characterized by days of the week. On the other hand, the daily calendar should be used when there is a yearly effect but not a weekly effect in the data (for example weather data). When both effects are present, the monthly calendar would be a better choice.

### 2017-08-08 main.tex
updated after today's meeting
update caption

\begin{equation}
  \begin{aligned}
  i &= \lceil (g\,\mod 35) / 7\rceil, \\
  j &= g\,\mod 7. \label{eq:grid}
  \end{aligned}
\end{equation}

@@

\caption[Illustration of the indexing layout for months of
one year. \(M,N\) indicate number of rows and columns, \(b\) is a space
parameter separating cells.]{Illustration of the indexing layout for months of
one year. \(M,N\) indicate number of rows and columns, \(b\) is a space
parameter separating cells.}\label{fig:year-diagram}
\end{figure}
\end{CodeChunk}

@@

The algorithm described in Section \ref{sec:algorithm} is for the most
common calendar layout, the ``monthly'' calendar, but it can be
simplified to accommodate two other types calendar formats. One is
comprised of days of a week in columns and weeks of a year in rows, and
the other is days of a month in columns and months of a year in rows,
which we refer to as the ``weekly'' and ``daily'' calendar,
respectively. The layout to be used is controlled by the \code{calendar}
argument. The weekly calendar puts more emphasis on days of a week over
days of a year, whereas the daily calendar does the opposite. The
monthly calendar can be considered as the advanced variant of both
weekly and daily. Temporal patterns motivate which variant should be
employed. The weekly calendar is appropriate if most of the variation
can be characterised by days of the week. On the other hand, the daily
calendar should be used when there is a yearly effect but not a weekly
effect in the data (for example weather data). When both effects are
present, the monthly calendar would be a better choice.

>>>>

\begin{equation}
  \begin{aligned}
  i &= \lceil (g \text{ mod } 35) / 7\rceil, \\
  j &= g \text{ mod } 7. \label{eq:grid}
  \end{aligned}
\end{equation}

@@

\caption[Illustration of the indexing layout for months of
one year, where \(M\) and \(N\) indicate number of rows and columns,
\(b\) is a space parameter separating cells.]{Illustration of the indexing layout for months of
one year, where \(M\) and \(N\) indicate number of rows and columns,
\(b\) is a space parameter separating cells.}\label{fig:year-diagram}
\end{figure}
\end{CodeChunk}

@@

The algorithm described in Section \ref{sec:algorithm} is for the most
common calendar layout, the ``monthly'' calendar, but it can be
simplified to accommodate two other types calendar formats. One is
comprised of days of a week in columns and weeks of a year in rows, and
the other is days of a month in columns and months of a year in rows,
which we refer to as the ``weekly'' and ``daily'' calendar,
respectively. The layout to be used is controlled by the \code{calendar}
argument. The weekly calendar puts more emphasis on days of a week over
days of a year, whereas the daily calendar does the opposite. The
monthly calendar can be considered as the advanced variant of both
weekly and daily. Temporal patterns motivate which variant should be
employed. The weekly calendar is appropriate if most of the variation
can be characterized by days of the week. On the other hand, the daily
calendar should be used when there is a yearly effect but not a weekly
effect in the data (for example weather data). When both effects are
present, the monthly calendar would be a better choice.
